Multi-resolution Neural Field Estimation

### 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
minor edit for  EM
put theta in line

where $\beta$ is constant with respect to $\boldsymbol\theta$. Equation \eqref{eq:Qfunction} is maximum at
 \boldsymbol \theta= \boldsymbol\Upsilon^{-\top}(\boldsymbol\upsilon_0^\top-\boldsymbol\upsilon_1^\top),
where

@@

where $[.]_{p:} $ denotes $p^{th}$ row of the matrix. All blocks of $\Gamma_1$,$\Gamma_2$ and $\Gamma_3$  can be computed as a once-off before the commencement of the EM iterations. Note that to separate $\boldsymbol\theta$ from $\boldsymbol\Lambda_{\theta}$ in forming the $\mathcal{Q}$-function we used the relation

@@

\left[ \boldsymbol\Lambda_{\theta}\right] _{i,j} =\left[ \mathbf U\right]^{i,j}\boldsymbol\theta

@@

\cut{The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}}. \ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165]. (This is copy and paste from my thesis ... parham I'll get you the references later)}. \parham{Mike,Ken: can add to this list?}

>>>>

where $\beta$ is constant with respect to $\boldsymbol\theta$. Equation \eqref{eq:Qfunction} is maximum at $\boldsymbol \theta= \boldsymbol\Upsilon^{-\top}(\boldsymbol\upsilon_0^\top-\boldsymbol\upsilon_1^\top)$ where
% \begin{align}
%  \boldsymbol \theta= \boldsymbol\Upsilon^{-\top}(\boldsymbol\upsilon_0^\top-\boldsymbol\upsilon_1^\top),
% \end{align}
% where

@@

where $[.]_{p:} $ denotes $p^{th}$ row of the matrix. All $n_x^2$ blocks of $\Gamma_1$,$\Gamma_2$ and $\Gamma_3$  can be computed as a once-off before the commencement of the EM iterations. Note that to separate $\boldsymbol\theta$ from $\boldsymbol\Lambda_{\theta}$ in forming the $\mathcal{Q}$-function we used the relation

@@

\left[ \boldsymbol\Lambda_{\theta}\right] _{i,j} =\left[ \mathbf U\right]^{i,j}\boldsymbol\theta, 

@@

 \cut{The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}}.

%  \ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165]. (This is copy and paste from my thesis ... parham I'll get you the references later)}. \parham{Mike,Ken: can add to this list?}
